VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-19 snapshot_system/paper_eval.tex
revise

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
our scheme achieves a 85K:1 ratio between raw snapshot data and memory usage 
with 96\% deduplication efficiency
while the sampled index method achieves 20K:1 (10GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increases to about 220MB. 
Notice that the sampled index method is designed for single-machine deduplication.
%and it is not easy to extend to a distributed cluster architecture.

>>>>

Comparing the experiment results of the sampled index method reported in~\cite{Guo2011}, 
our scheme achieves a 85K:1 ratio between raw snapshot data and memory usage 
with 96\% deduplication efficiency
while the sampled index method achieves 20K:1 (25GB memory per 500TB raw data)
with 97\% deduplication efficiency.
Thus our scheme is more memory efficient with a good tradeoff for deduplication efficiency.
If we change $\sigma=4\%$, the deduplication efficiency of VC increases to 96.58\% while
memory usage per machine increases to about 220MB. 
Notice that the sampled index method is designed for single-machine deduplication.
%and it is not easy to extend to a distributed cluster architecture.
